%%% The main file. It contains definitions of basic parameters and includes all other parts.

%% Settings for single-side (simplex) printing
% Margins: left 40mm, right 25mm, top and bottom 25mm
% (but beware, LaTeX adds 1in implicitly)
\documentclass[12pt,a4paper]{report}
\setlength\textwidth{145mm}
\setlength\textheight{247mm}
\setlength\oddsidemargin{15mm}
\setlength\evensidemargin{15mm}
\setlength\topmargin{0mm}
\setlength\headsep{0mm}
\setlength\headheight{0mm}
% \openright makes the following text appear on a right-hand page
\let\openright=\clearpage

%% Settings for two-sided (duplex) printing
% \documentclass[12pt,a4paper,twoside,openright]{report}
% \setlength\textwidth{145mm}
% \setlength\textheight{247mm}
% \setlength\oddsidemargin{14.2mm}
% \setlength\evensidemargin{0mm}
% \setlength\topmargin{0mm}
% \setlength\headsep{0mm}
% \setlength\headheight{0mm}
% \let\openright=\cleardoublepage

%% Generate PDF/A-2u
\usepackage[a-2u]{pdfx}

%% Character encoding: usually latin2, cp1250 or utf8:
\usepackage[utf8]{inputenc}

%% Prefer Latin Modern fonts
\usepackage{lmodern}

%% Further useful packages (included in most LaTeX distributions)
\usepackage{amsmath}        % extensions for typesetting of math
\usepackage{amsfonts}       % math fonts
\usepackage{amsthm}         % theorems, definitions, etc.
\usepackage{bbding}         % various symbols (squares, asterisks, scissors, ...)
\usepackage{bm}             % boldface symbols (\bm)
\usepackage{graphicx}       % embedding of pictures
\usepackage{fancyvrb}       % improved verbatim environment
\usepackage[square,numbers]{natbib}         % citation style AUTHOR (YEAR), or AUTHOR [NUMBER]

\usepackage[nottoc]{tocbibind} % makes sure that bibliography and the lists
			    % of figures/tables are included in the table
			    % of contents
\usepackage{dcolumn}        % improved alignment of table columns
\usepackage{booktabs}       % improved horizontal lines in tables
\usepackage{paralist}       % improved enumerate and itemize
\usepackage{xcolor}         % typesetting in color
\usepackage{float}
\usepackage{listings}
\usepackage{color}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{marginnote}
\usepackage{hyperref}
\usepackage{cleveref}

%%% Basic information on the thesis

% Thesis title in English (exactly as in the formal assignment)
\def\ThesisTitle{A Methodical Approach to the Evaluation of Appearance Computations}

% Author of the thesis
\def\ThesisAuthor{Bc. Marcel Hruška}

% Year when the thesis is submitted
\def\YearSubmitted{2020}

% Name of the department or institute, where the work was officially assigned
% (according to the Organizational Structure of MFF UK in English,
% or a full name of a department outside MFF)
\def\Department{Department of Software and Computer Science Education}

% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Department}

% Thesis supervisor: name, surname and titles
\def\Supervisor{doc. Alexander Wilkie, Dr.}

% Supervisor's department (again according to Organizational structure of MFF)
\def\SupervisorsDepartment{Department of Software and Computer Science Education}

% Study programme and specialization
\def\StudyProgramme{Computer Science}
\def\StudyBranch{Computer Graphics and Game Development}

% An optional dedication: you can thank whomever you wish (your supervisor,
% consultant, a person who lent the software, etc.)
\def\Dedication{%
I would like to express my sincere gratitude to my supervisor doc. Alexander Wilkie, Dr., for all the patience, help and advice he has given me.

I want to thank my girlfriend, my family and my friends for their constant support, especially during the last half year.
}

% Abstract (recommended length around 80-200 words; this is not a copy of your thesis assignment!)
\def\Abstract{%
Many techniques for the computation of realistic images exist, and there are a number of key technical aspects to
such systems. In addition to the light transport technique which is being used, the details of how description and
computation of object appearance are key distinguishing features. The details in questions span a wide range of
features, such as the list of BRDF and BSSDF models which are supported in a given system, to the question
whether computations are performed in color space or in spectral form, to whether features such polarization or
fluorescence are being supported. Although there are obvious similarities between systems, there is no standardized
implementation of any of these features, and their computation might vary in terms of accuracy.

Currently, whenever a researcher works on any aspect of appearance computation, they demonstrate their findings
on their own set of test scenes. These scenes might not necessarily cover all test scenarios, and any possible
inaccuracies might not be exposed properly.

So there is a need for an appearance test suite that would assess the correctness of such computations. The goal of
this thesis is to introduce such a set of scenes that can be used to methodically test rendering algorithms based on
their appearance reproduction capabilities. The test scenes are created in such a manner that they examine the
capabilities of the appearance computations to correctly render respective features, while neglecting other aspects
of rendering, such as global illumination. With the appearance in mind, we focus on spectral rendering in general,
as well as specialized forms of it, such as fluorescence, dispersion or polarization. For various test cases, we
manually verify that the reference images display proper results according to the definition of respective features.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces
\def\Keywords{%
{appearance},{evaluation},{spectral rendering},{iridescence},{polarization},\\{fluorescence}
}

%% The hyperref package for clickable links in PDF and also for storing
%% metadata to PDF (including the table of contents).
%% Most settings are pre-set by the pdfx package.
\hypersetup{unicode}
\hypersetup{breaklinks=true}

% Definitions of macros (see description inside)
\include{macros}

% Title page and various mandatory informational pages
\begin{document}
\include{title}

%%% A page with automatically generated table of contents of the master thesis

\tableofcontents

%%% Each chapter is kept in a separate file
\include{preface}
\include{color_science}
\include{appearance}
\include{benchmark}
\include{results}

\include{epilog}

%%% Bibliography
\include{bibliography}

%%% Figures used in the thesis (consider if this is needed)
%%%\listoffigures

%%% Tables used in the thesis (consider if this is needed)
%%% In mathematical theses, it could be better to move the list of tables to the beginning of the thesis.
%%%\listoftables

%%% Abbreviations used in the thesis, if any, including their explanation
%%% In mathematical theses, it could be better to move the list of abbreviations to the beginning of the thesis.
%%%\chapwithtoc{List of Abbreviations}

%%% Attachments to the master thesis, if any. Each attachment must be
%%% referred to at least once from the text of the thesis. Attachments
%%% are numbered.
%%%
%%% The printed version should preferably contain attachments, which can be
%%% read (additional tables and charts, supplementary text, examples of
%%% program output, etc.). The electronic version is more suited for attachments
%%% which will likely be used in an electronic form rather than read (program
%%% source code, data files, interactive charts, etc.). Electronic attachments
%%% should be uploaded to SIS and optionally also included in the thesis on a~CD/DVD.
%%% Allowed file formats are specified in provision of the rector no. 72/2017.
\appendix
\chapter{User Guide}
\label{user_guide}
The user may clone/download the benchmark from the github repository \url{https://github.com/marcel1hruska/render_benchmark} or he can find it in the attachments of thesis~\ref{sec:benchmark}. As the whole benchmark is written in Python3, there is no need to compile the project. 

Firstly, it is necessary to modify \texttt{settings.json} file in the root directory of the benchmark suite --- the user must specify the path to the renderer executable and the name of the renderer (currently, the only viable options are \texttt{mitsuba2} and \texttt{ART}).

After that, the benchmark can be run with a simple invocation of the \\ \texttt{benchmark.py} python file. 
The benchmark accepts several parameters:
\begin{description}
	\item[-{}-help (-h)] Prints the help message
	\item[-{}-scene (-s) \textless scene\_name\textgreater] Test only the scene called scene\_name
	\item[-{}-case (-c) \textless test\_case\_name\textgreater] Test only the test case called test\_case\_name
	\item[-{}-renderer (-r) \{ART\(|\)mitsuba2\}] Specify the name of the renderer 
	\item[-{}-exec (-e) \textless path\textgreater] Specify the path to the renderer executable
	\item[-{}-log (-l)] Write all outputs to the log file (in the outputs folder) instead of the console
	\item[-{}-visualize (-v)] Visualize the outputs immediately after the benchmark ends
\end{description}

For the user's convenience, all of these options may be specified in the \\ \texttt{settings.json} file but the ones issued in the CLI take higher priority and override them.

As soon as the benchmark ends, the user may find the rendered EXR images in a folder named \texttt{outputs-yyymmdd-hhmmss} where \texttt{yyymmdd-hhmmss} is substituted for the date and the time when the command was issued.

Then, the user may invoke a second script, \texttt{visualize.py}, that opens a website with the results of the last benchmark run along with the reference images and their difference images.

\begin{description}
	\item[-{}-help (-h)] Prints the help message
	\item[-{}-outputs (-o) \textless output\_folder\_name\textgreater] Specify the name of the\\ \texttt{outputs-yyymmdd-hhmmss} folder that is to be visualized. If omitted, the latest folder is picked.
\end{description}


\chapter{Attachments}

All attachments are listed below and can be found in the \texttt{attachments} folder. 

\section{Benchmark}
\label{sec:benchmark}

Contains the whole testing suite, can also be downloaded from \url{https://github.com/marcel1hruska/render_benchmark}. If the user downloaded the thesis from github, he needs to do so recursively as the \texttt{render\_benchmark} is a submodule.

\section{Iridescence for Mitsuba2}
\label{sec:mitsuba2_irid}

Contains the iridescence implementation for Mitsuba2. The folder can be simply copied over the Mitsuba2 code version 2.1.0. Note that only the \texttt{iridescence.h} and \texttt{iridescence.cpp} files contain our code --- the rest of the code mostly belongs to Mitsuba2 and only small parts that activate the iridescent effects were created by us. 

To make matters more simple, we created a forked repository on \url{https://github.com/marcel1hruska/mitsuba2}. The user needs to checkout the \\ \texttt{iridescence} branch and compile it accordingly to the Mitsuba2 documentation~\cite{mitsubaWeb}.

\section{GGX for ART}
\label{sec:ggx_art}

Contains the GGX implementation for ART. The folder can be simply copied over the ART code version 2.0.3. Note that the files also include the implementation of the Blinn microfacet distribution which belongs to ART and is not a part of this thesis. 

Unfortunately, we do not have a fork of the repository as the origin is not on github.

\openright
\end{document}
